Portal Forecast

### 2017-09-27 index.Rmd
putting plot of most recent data against forecast on website (#111)
* changed name of plot_data function to plot_species_forecast for clarity

* added code to plot the most recent data from the repo against the most recent forecast prior to that data collection.  there are still some issues, right now this will only work when June 2017 is the most recent data

* removed old code from report.Rmd

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
plot_data(sp_predictions)
```
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE}
most_abund_sp = sp_predictions %>% 
  filter(species != 'total') %>% 
  arrange(desc(estimate)) %>% 
  head(3) %>% 
  select(species)

>>>>

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions)
plot(sp_predict)
```
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE}
most_abund_sp = sp_predictions %>% 
  filter(species != 'total') %>% 
  arrange(desc(estimate)) %>% 
  head(3) %>% 
  select(species)
